\section{Literaturverzeichnis}
Al Abed, W. und Kienzle J. (2009): Information Hiding and Aspect-Oriented Modeling\\\\
Atlassian Support (© 2025) [Online]. Verfügbar unter https://support.atlassian.com (Abgerufen am 24. Januar 2025)\\\\
Fensel, D. et al. (2020) Knowledge graphs: methodology, tools and selected use cases, Berlin, Springer Verlag\\\\
Jarrahi M. et al. (2023) Artificial intelligence and knowledge management: A partnership between human and AI, Amsterdam NL, Elsevir \\\\
Koleoso, T. (2020) Beginning Quarkus Framework: Build Cloud-Native Enterprise Java Applications and Microservices, Berkeley, CA, Apress\\\\
Quarkus (© 2024): What is Quarkus? [Online]. Verfügbar unter https://quarkus.io/about (Abgerufen am 11. November 2024)\\\\
Schobert, M. et al. (2024) Unveiling Causality in Stateful Enterprise Knowledge Graphs: An Exploration of Process-Driven Object Relationships, Amsterdam NL, Elsevir\\\\
Robinson, I., Webber, J. und Eifrem, E. (2015) Graph Databases: New opportunities for connected data, 2. Aufl., Sebastopol CA USA, O'Reilley\\\\
Seacord, R. und Wrage L. (2002) Replaceable Components and the Service Provider Interface [Online], Pittsburgh USA, Carnegie Mellon University. Verfügbar unter https://insights.sei.cmu.edu/documents/1994/2002\_004\_001\_13958.pdf\\\\
Tremp, H. (2022)  Agile objektorientierte Anforderungsanalyse:  Planen – Ermitteln – Analysieren – Modellieren – Dokumentieren – Prüfen, Wiesbaden, Springer Verlag\\\\
Vaisman, A. und Zimányi, E. (2022) Data Warehouse Systems: Design and Implementation, 2. Aufl., Berlin, Springer Verlag\\\\
van Steen, M., Pierre, G. und Voulgaris, S. (2012) Challenges in very large distributed systems. J Internet Serv Appl 3, 59–66. https://doi.org/10.1007/s13174-011-0043-x\\\\
Jira Software Essentials: Plan, track, and release great applications with ...